Predicting Spotify Audio Features from Last.fm Tags

### 2023-07-01 paper/main.tex
add abstract and piece of conclusions

\affil[1]{\orgdiv{Departamento de Sistemas Informáticos}, \orgname{Universidad de Castilla-La Mancha}, \orgaddress{\street{Campus universitario s/n}, \city{Albacete}, \postcode{02071}, \country{Spain}}}

@@

\abstract{
    In this paper, we discuss a number of experiments to analyze the
    suitability of music label representations to predict certain audio features,
    such as danceability, loudness, or acousticness \dots
}

@@

      \caption{Experiment results. Cells values correspond to the RMSE value.}\label{table:experiment_results}%

@@

\textcolor{red}{TODO: as you have std deviations for your RMSE, can you say that
.291 is really better than .297 ? (idem for other results)}

@@

>>>>

@@

\abstract{
      Music information retrieval (MIR) is an interdisciplinary research field that focuses on the extraction, processing,
      and knowledge discovery of information contained in music.
      While previous studies have utilized Spotify audio features
      and Last.fm tags as input values for classification tasks, such as music genre recognition,
      their potential as target values has remained unexplored.
      In this article, we address this notable gap in the research landscape by proposing a novel approach to predict
      Spotify audio features based on a set of Last.fm tags.
      By predicting audio features, we aim to explore the relationship between subjective perception and concrete musical features,
      shedding light on patterns and hidden correlations between how music is perceived, consumed, and discovered.
      Additionally, the predicted audio features can be leveraged in recommendation systems
      to provide users with explainable recommendations, bridging the gap between algorithmic suggestions and user understanding.
      Our experiments involve training models such as GPT-2, XGBRegressor, and Bayesian Ridge regressor to predict
      Spotify audio features from Last.fm tags.
      Through our findings, we contribute to the advancement of MIR research by demonstrating the potential of Last.fm
      tags as target values and paving the way for future research on the connection between subjective and objective music characterization.
      Our approach holds promise for both listeners and researchers,
      offering new insights into the intricate relationship between perception and audio signal in music.
}

@@

      \caption{Experiment results. Cells values correspond to the RMSE value.
      Highlighted values correspond to the best RMSE value achieved by each model, for each variable.}
      \label{table:experiment_results}%

@@

@@

The standard deviation values that are displayed in figure \ref{fig:rmse_by_feature_and_input} are in the 0.1-0.2 margin.
Considering this factor, we argue that the RMSE values that some models manifest are, in fact, noteworthy.
For example, the best value for instrumentalness is \num{0.291}.
Considering that the mean and standard deviation for all the experiments with this variable are, respectively,\num{0.414} and\num{0.106}, the z-scores
of \num{0.291} and \num{0.297} are \num{-1.16} and \num{-1.10}.
We can conclude that the \num{0.291} and \num{0.297} values are close to each other and exhibit a similar level of deviation from the mean.
